---
title: "BA_ASSIGNMENT 3"
author: "Yeswanth Siripurapu"
date: "2023-11-06"
output:
  word_document: default
  html_document: default
  pdf_document: default
---
#Run the following code in R-studio to create two variables X and Y
```{r}
set.seed(2017)
X <- runif(100) * 10
Y <- X * 4 + 3.45
Y <- rnorm(100) * 0.29 * Y + Y

```

```{r}
set.seed(2017)
X <- runif(100) * 10
Y <- X * 4 + 3.45
Y <- rnorm(100) * 0.29 * Y + Y

plot(X, Y, main = "Scatter plot of Y against X", xlab = "X", ylab = "Y")

```

#b) Construct a simple linear model of Y based on X. Write the equation that 
#explains Y based on X. What is the accuracy of this model
```{r}
model <- lm(Y ~ X)
summary(model)

```
#C)How the Coefficient of Determination, R 2, of the model above is related to
#the correlation coefficient of X and Y? R-squared (R2) and the correlation coefficient (r) have the following
#relationships:The square of the correlation coefficient (r) is known as R-squared (R²). 
#In this instance, the linear relationship with X accounts for roughly 65.17% of
#the variance in Y, as indicated by the R2 of approximately 0.6517.

#The degree and direction of the linear link between X and Y are measured by the
#correlation coefficient (r). The value of r in a basic linear regression is
#obtained under "Estimate" and is equal to the coefficient for X (3.6108 in
#the output).

#Accordingly, in this instance, the coefficient of determination (R2) is roughly
#0.6517 and the correlation coefficient (r) is roughly 3.6108. The percentage of
#Y's volatility that can be predicted from X is represented by R².


#QUESTION 2
#a) James wants to buy a car. He and his friend, Chris, have different 
#opinions about the HorsePower (hp) of cars. James think the weight of a car 
#(wt) can be used to estimate the Horse Power of the car while Chris thinks the
#fuel consumption expressed in Mile Per Gallon (mpg), is a better estimator of 
#the (hp). Who do you think is right? Construct simple linear models usingmtcars
#data to answer the question.

#Building a model based on James estimation:
```{r}
# Load the mtcars dataset 
data(mtcars)

# Construct a linear model using weight (wt) to estimate horsepower (hp)
model_wt_hp <- lm(hp ~ wt, data = mtcars)
summary(model_wt_hp)
```


```{r}
# Construct a linear model using mileage per gallon (mpg) to estimate horsepower (hp)
model_mpg_hp <- lm(hp ~ mpg, data = mtcars)
summary(model_mpg_hp)
```
#The link between horsepower and fuel efficiency (mpg) appears to have a greater
#R-squared value than the association between horsepower and vehicle weight (wt),
#according to the R-squared values obtained from the linear regression models.
#Since fuel consumption (mpg) is a better predictor of horse power (hp) and fits
#the dataset better for predicting hp, it appears that Chris's point of view is
#more valid.



#b) Build a model that uses the number of cylinders (cyl) and the mile per 
#gallon (mpg) values of a car to predict the car Horse Power (hp). Using this 
#model, what is the estimated Horse Power of a car with 4 calendar and mpg of 
#22?


```{r}
# Build the model using cyl and mpg to predict hp
model_cyl_mpg <- lm(hp ~ cyl + mpg, data = mtcars)

# Summary of the model
summary(model_cyl_mpg)
```
#Based on this, the estimated Horse Power of a car with 4 cylinders and mpg of 
#22 is approximately 88.93618


#Question 3. For this question, we are going to use BostonHousing dataset. The dataset is
#in ‘mlbench’ package, so we first need to install the package, call the library
#and load the dataset using the following commands
```{r}
# Predicting hp for a car with 4 cylinders and mpg of 22
new_data <- data.frame(cyl = 4, mpg = 22)
predict(model_cyl_mpg, newdata = new_data)
```


```{r}
# Load the mlbench library
library(mlbench)
```

```{r}
# Load the Boston Housing dataset
data(BostonHousing)
```
#a) Build a model to estimate the median value of owner-occupied homes (medv)
#based on the following variables: crime crate (crim), proportion of residential 
#land zoned for lots over 25,000 sq.ft (zn), the local pupil-teacher ratio
#(ptratio) and weather the whether the tract bounds Chas River(chas). Is this
#an accurate model?
```{r}
# Build the linear regression model
model_medv <- lm(medv ~ crim + zn + ptratio + chas, data = BostonHousing)

# Summary of the model
summary(model_medv)
```
#b) Use the estimated coefficient to answer these questions?
#I. Imagine two houses that are identical in all aspects but one bounds the Chas
#River and the other does
#not. Which one is more expensive and by how much?

#Answer: Chas has two levels: '0' and '1'. Those who cross the Chas River are
#denoted by a "1," while those who do not are denoted by a "0."The data 
#description states that the median value of owner-occupied dwellings is $1,000,
#and the coefficient of chas1 is 4.58393. The product of coefficient and
#multiplier is 4583.93$. this costs a lot.

#II. Imagine two houses that are identical in all aspects but in the neighborhood
#of one of them the pupilteacher ratio is 15 and in the other one is 18. Which 
#one is more expensive and by how much?

#Answer: In thousands, the price of a house decreases by 1.49367, or 1493.67, for
#If ptratio is 15. Likewise, there will be a drop of 18 * 1493.67 = 26886.06 if
#ptratio is 18.Therefore, if the pt ratio is 15 and the pt ratio is 18, the
#difference is $4481.01.
 
#c) Which of the variables are statistically important (i.e. related to the 
#house price)? Hint: use the p-values of the coefficients to answer.

#Answer: Indeed, we can safely reject the default null hypothesis—that is, the
#idea that there is no relationship between house price and other factors in the #model—because the p-values of all the variables do not equal zero. All of the 
#factors are therefore statistically significant.

#d) Use the anova analysis and determine the order of importance of these four
#variables
```{r}
# ANOVA analysis for the model
anova_result <- anova(model_medv)

# Display the ANOVA table
anova_result
```
#Answer: It is evident that the crim variable explains a substantially larger
#amount of variability (sum squared) than the other factors. We could surmise 
#that the model was greatly enhanced by the addition of the crim. However,
#residuals indicate that a significant amount of variability remains unexplained.
#The significance is as follows: crim, p tratio, zn, chas
